Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-28 src/article.tex
Correct punctutation in conclusions

Scaffolder follows the Unix philosophy of ``Do one thing and do it well''. The
focus of Scaffolder is a simple to use tool for creating a genome scaffold. The
YAML data format for creating the scaffold file is standardised and easily
manipulated programmatically. This thereby means the scaffolding process
follows a second Unix tenet: ``If your data structures are good enough, the
algorithm to manipulate them should be trivial.''

>>>>

Scaffolder follows the Unix philosophy of ``Do one thing and do it well.''. The
focus of Scaffolder is a simple to use tool for creating a genome scaffold. The
YAML data format for creating the scaffold file is standardised and easily
manipulated programmatically. This thereby means the scaffolding process
follows a second Unix tenet: ``If your data structures are good enough, the
algorithm to manipulate them should be trivial.''.
